Extended Data

### 2021-10-21 doc/manuscript/Dow_manuscript_Nature.Rmd
removed details on phenological advances, now in Table S2.
@camerondow35 , good suggestion!

For ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the critical temperature window resulted in earlier achievement of growth milestones (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Consistent with findings from previous studies[@parmesan_globally_2003, @ibanez_forecasting_2010,@friedl_tale_2014], the DOY of leaf greenup advanced with increasing $T_{max}$ during the critical temperature window (p= 0.001 at SCBI; p= 0.1 at HF). 
Specifically, greenup DOY advanced 4.5 days/$^\circ$C at SCBI and 2.4 days/ $^\circ$C at Harvard Forest, and mid-greenup also advanced, but to a lesser extent (Fig. `r DOY_timing`).
Similarly, at both sites, $DOY_{25}$, $DOY_{50}$, $DOY_{75}$, and $DOY_{g_{max}}$ all decreased with mean $T_{max}$ during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`; `r EDF_pheno_all`).
Specifically, at SCBI, RP growth advanced 1.9, 1.5, and 1.1 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively, while DP growth advanced 3.5, 3.5, and 3.6 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively.
At Harvard Forest, RP growth advanced 2.8, 5.0, and 7.2 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively, while DP growth advanced 7.9, 7.3, and 6.6 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively. *(This might be better as a table. Add to an existing one? May be able to add to mean_growth_parameters table)*

>>>>

For ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the critical temperature window resulted in earlier achievement of growth milestones (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Consistent with findings from previous studies[@parmesan_globally_2003, @ibanez_forecasting_2010,@friedl_tale_2014], the DOY of leaf greenup advanced with increasing $T_{max}$ during the critical temperature window (p= 0.001 at SCBI; p= 0.1 at HF). 
Specifically, greenup DOY advanced 4.5 days/$^\circ$C at SCBI and 2.4 days/ $^\circ$C at Harvard Forest, and mid-greenup also advanced, but to a lesser extent (Fig. `r DOY_timing`, `r EDT_phenology_parameters`).
Similarly, at both sites, $DOY_{25}$, $DOY_{50}$, $DOY_{75}$, and $DOY_{g_{max}}$ all decreased with mean $T_{max}$ during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`; `r EDF_pheno_all`).
Specifically, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ advanced 1.1-1.9 days/ $^\circ$C for ring-porous species and 3.5-3.6 days/ $^\circ$C for diffuse-porous species at SCBI, and 2.8-7.2 days/ $^\circ$C for ring-porous species and 6.6-7.9 days/ $^\circ$C for diffuse-porous species at Harvard Forest (`r EDT_phenology_parameters`).
